Test

### 2020-08-15 paper.tex
new title and abstract

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Data-Driven Customization of Web Applications}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Customizing software should be as easy as using it. But most
  customization methods require a dramatic shift, from using a GUI to
  writing scripts in a programming language.

  We introduce \emph{data-driven customization}, a new way for end users
  to extend software by direct manipulation without doing traditional
  programming. We augment existing user interfaces with a table view
  showing the structured data inside the application. When users edit
  the table, their changes are reflected in the original UI. This simple
  model accommodates a spreadsheet formula language and custom data
  editing widgets, providing enough power to implement a variety of
  useful extensions.

  We illustrate the approach with Wildcard, a browser extension that
  implements data-driven customization on the web using web scraping.
  Through concrete examples, we show that this paradigm can support
  useful extensions to many real websites, and we share reflections from
  our experiences using Wildcard.

  Finally, we share our broader vision for a future where end users have
  greater access to the data in their applications, and better tools for
  taking advantage of that data in the context of everyday software
  usage.
\end{abstract}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Test}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Test.
\end{abstract}
